\chapter{Project Methodology}
In this chapter we will describe the project methodology that we have applied to this project.
We will first divide the project into three phases.
For each phase we will specify the goal of this phase, the planning, the process strategy, the planned deliverables and the project roles.
Lastly, we define the tools that we have used during the project.
We have chosen for this particular form of documentation because in this way we can easily describe the unique aspects of each phase.

\section{Global planning}
We have set up a global planning that splits up the project in phases.
Each of these phases has deliverables attached to them.
We will be mentioning our goals for each week.
Other important dates are also added to the planning.

In the image below you can see the global planning that we have set up.
It mentions all the big deliverables and gives the team a good overview of how far the progress of the project should be.
The team can compare the current state of the project with this planning and can conclude if there is sufficient progress and if measures should be undertaken.
%Todo add image of the global planning

\section{Overall process strategy}
During this phase we choose to not have a strict task distribution.
Many of the tasks at hand needed group thinking and group opinions.
For example, the interpretation of the problem description is something that can be thought out by a single person, but needs to be communicated about toward the other team members.
If not communicated enough, the resulting problem description may not be the same as how the team interpreted the client's description.
Things that needed to be done were documented in a spreadsheet.
In this way, every team member had insight into the things that still needed to be done.

\subsection{Software development method}
During the implementation phase we used a known software development framework.
This development framework is known as scrum.
Scrum is based on the agile software development framework which can be used to 
manage software projects.
The time that we have to implement the system is limited so we did not have the time to research and design all aspects of the system. We need a software development framework that gave us the possibility to react to changes in requirements, but also to react to new insights given by our increasing understanding of the system as time progresses.
Scrum has a flexible approach to software development and satisfies the requirements that we have mentioned above.
In scrum, you only need a basic design of the system before you start implementing.
During implementation you provide daily feedback on your progress and the team can change the way things are programmed or have been programmed to steer the product in the proper direction.
We have defined the different roles associated with scrum (e.g. the product owner, development team, scrum master) as you can see below.

\section{Project roles}
As said above, there was not a strict task distribution.
Following the advise of our group mentor, every week a different team member was the designated chairman and another team member was the designated secretary.
The chairman of the week had the responsibility to preside the weekly meetings and to maintain an overview of the tasks that were at hand.
The secretary had the responsibility of making minutes of both the weekly meetings and the meetings with the group mentors and client.
Next to these two roles, there were no other defined roles.

The following table lists the different group members, their roles and a short description.
This description describes the role and responsibilities of the group member.\\
\begin{tabular}{|l|l|p{5cm}|}
\hline
Name & Roles & Description\\
\hline
Freek van Tienen & Lead Development & Responsible for implementation phase.\\
\hline
Floris Verburg & Scrum master and Quality Assurance & Responsible for the Scrum process, the quality of the code and test coverage.\\
\hline
Marijn Goedegebure & Project Manager and Reports & Manages the project and ensures that the requirements are met.\\
\hline
\end{tabular}

\section{Phase 1}
\subsection{Goal}
The first phase aims to expand the knowledge of the group about the problem and it's requirements.
Secondly, it also gives time for the team members to analyse the problem for difficult subjects and to spend time finding a fitting solution.
Thirdly it gives the team members the time to set up the project infrastructure and to define the project methodology.
Lastly, the remaining time should be spend making a first start with the system design.

\subsection{Planning}
We planned phase 1 to be two weeks long.
With the first week having a focus on setting up the project and doing research to the problem and requirements.
The second week was more about defining the project methodology, analysing and researching the possible problems that we could encounter and making a first system design.
The second week was also used to finish up the research report.
\subsubsection{Planned deliverables}
At the end of phase 1 we wanted to have the following deliverables done:
\begin{itemize}
\item Research report
\item Plan of approach
\item First system design
\end{itemize}

\subsection{Process strategy}
During this phase we choose to not have a strict task distribution.
Many of the tasks at hand needed group thinking and group opinions.
For example, the interpretation of the problem description is something that can be thought out by a single person, but needs to be communicated about toward the other team members.
If not communicated enough, the resulting problem description may not be the same as how the team interpreted the client's description.
Things that needed to be done were documented in a spreadsheet.
In this way, every team member had insight into the things that still needed to be done.

\subsection{Phase reflection}
%Nog te doen: schrijven over het verloop van deze phase

\section{Phase 2}
\subsection{Goal}
The purpose of the second phase was to provide a time frame in which both a basic system design can be made and the system design could be implemented.
During the second phase the roles were more strict since we wanted to follow a structured software development method.
This software development method is the framework known as scrum.
We will go into depth about this in the process strategy section.

\subsection{Planning}
We planned the second phase to be six weeks long.
The first week would be used to finish up the system design.
The other 5 weeks will be used to implement this system design.
During the final two weeks we looked into the user tests and the acceptance tests.
During this time there we also sent our source code to the Software Improvement Group for them to check.
The feedback that we got back will be 

\subsubsection{Planned deliverables}
During phase two we wanted to have the following deliverables done:
\begin{itemize}
\item Basic system design
\item User tests
\item Send the source code to SIG for the first review
\end{itemize}

\subsection{Phase reflection}
%Nog te doen: schrijven over het verloop van deze phase

\section{Phase 3}
\subsection{Goal}
The goal of the third and last phase is to provide for time to finish up the project.
During this phase time has been reserved for finishing up the implementation, the final report and for the user tests.

\subsection{Planning}
During this phase there is time for completion of the implementation, finalization of the final report and creation of the presentation.
The completion of the implementation and the finalization of the final report will been done simultaneously.
The creation of the presentation will be done after the final report has been submitted.
After the final report is submitted we will also be looking into the feedback that we received from the SIG.
Three days before the presentation, the source code should be send to SIG for a final review.

\subsubsection{Planned deliverables}
During phase three we wanted to have the following deliverables done:
\begin{itemize}
\item Final report
\item Presentation
\item Improved implementation following the comments provided by SIG
\item Final review of SIG
\end{itemize}

\subsection{Phase reflection}
%Todo, write a phase reflection	

\section{Tools}
We have used several tools to support our development.
They helped us to maintain the quality of the code and improve the maintainability.
Some of these tools also helped with structuring the implementation phase.

\begin{itemize}
\item IntelliJ IDEA, is our Integrated Development Environment (IDE) which will facilitate the development and testing of our code.
IntelliJ will be integrated with the Play framework which will be helpful during development.
\item GitHub, is our on-line code and documentation repository.
It provides for a version control system, an issue tracker and code review possibilities.
We will be using it to store all our code and documentation's code (LaTeX).
\item Cloudbees
Cloudbees will be used to run our test environment, our continuous integration and the release environment.
It uses Jenkins for the continuous integration.
\item Play framework
The play framework gives us the possibility to easily create a web application using Java.
\item Findbugs is a plug in for Cloudbees and IntelliJ that gives us the possibility to let our java code be checked for small bugs using static analysis.
\item JaCoCo is a plug in for Cloudbees and IntelliJ that provides us with data analysis about our code coverage.
\item Checkstyle is a plug in for Cloudbees and IntelliJ that checks the code for coding standards.
This makes it ideal to enforce the coding standard for our project.
\end{itemize}
